Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2016-10-14 salmon/paper/salmon_paper.Rmd
updates

@@

```{r, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying intercepts on estimated mean revenue, by permit. These are interpreted as the mean change in revenue for each permit holder in each year (positive equates to increasing revenue, etc), after accounting for effects of catch diversification and days fished."}
# grab original data to look at permit names
diffdat = readRDS(file="../../salmon/data-generated/salmon.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

yearpermit = data.frame("yrpermit"=levels(diffdat$year_permit))
yearpermit$year = as.numeric(substr(yearpermit$yrpermit,1,4))
yearpermit$permit = substr(yearpermit$yrpermit,6,9)

@@

```{r, fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on revenue (measured in ln dollars) for hypothetical individuals with species diversity ~ 1. This shows declining benefits of diversification for most fisheries, S01M.", echo=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../salmon/data-generated/salmon.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

@@

```{r, fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on log standard deviation of revenue for hypothetical individuals with species diversity ~ 1.", echo=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../salmon/data-generated/salmon.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

>>>>

- In terms of participation, why did people drop out in 2000 in SEAK and Alaska Peninsula, but not in PWS? PWS largely seems like a boutique fishery on the Copper River -- which includes a qualtiy component (Copper River at forefront) and a timing issue relative to the rest of the Gulf of Alaska populations (buffers against market impacts)

@@

```{r, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying intercepts on estimated mean revenue, by permit. These are interpreted as the mean change in revenue for each permit holder in each year (positive equates to increasing revenue, etc), after accounting for effects of catch diversification and days fished."}
# grab original data to look at permit names
diffdat = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

yearpermit = data.frame("yrpermit"=unique(diffdat$year_permit))
yearpermit$year = as.numeric(substr(yearpermit$yrpermit,1,4))
yearpermit$permit = substr(yearpermit$yrpermit,6,9)

@@

```{r, fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on revenue (measured in ln dollars) for hypothetical individuals with species diversity ~ 1. This shows declining benefits of diversification for most fisheries, S01M.", echo=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

@@

```{r, fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on log standard deviation of revenue for hypothetical individuals with species diversity ~ 1.", echo=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))
